\documentclass[10,twocolumn]{article}
\input{latex_utils/preamble.tex}
\begin{document}

\title{Dicex-pgsa: Managing Standalone Postgres in Supercomputer\\ 
User's Manual}

\maketitle

\paragraph{\question{How to obtain Dicex-pgsa?}}\hfill\\
For development clone the repo \url{https://ndsslgit.vbi.vt.edu/ndssl-software/dicex_pgsa}.
For use in your projects, login to shadowfax and run
\begin{lstlisting}[style=mystyle]
you@sfxlogin1: cd <your-work-directory>
you@sfxlogin1: . /home/pgxxc/public/dicex.sh
\end{lstlisting}

\paragraph{\question{How to launch  a job running a database instance?}}\hfill\\
\begin{lstlisting}[style=mystyle]
you@sfxlogin1: cd <your-work-directory>
dicex\_pgsa.sh --launchjob <session-identifier>
\end{lstlisting}
where $<$session-identifier$>$ is a tag that defines the current database session.  It is optional. 
If not provided, the system will assign an idenifier as ``pgsa\_YYYY\_MM\_DD\_HH''. 

This command grabs hold of a compute resource and launches a database engine on a port. 
The compute node is identified as server\_ip and the port as server\_port. Both of these
are writted on in the ``dbsession\_$<$session-identifier$>$.py'' file. 

\paragraph{\question{How to remove a job?}}\hfill\\
\begin{lstlisting}[style=mystyle]
you@sfxlogin1: cd <your-work-directory>
dicex\_pgsa.sh --removejob <session-identifier>
\end{lstlisting}

\paragraph{\question{Other Options}}\hfill\\
\begin{itemize}
\topsep=0pt\itemsep=0pt
\item To run a script after start of the database, use following additional option\hfill\\
\begin{lstlisting}[style=mystyle]
--post_dbstart <script_file_full_path>
\end{lstlisting}
where $<$postdb\_script$>$ is the path to the script being run.
\item To run a  script after the shutdown of the database, use following additional command\hfill\\
\begin{lstlisting}[style=mystyle]
--post_dbstop <script_file_full_path>
\end{lstlisting}
\item To close a database session (so that post\_dbstop script can be called use following command \hfill\\
\begin{lstlisting}[style=mystyle]
--closedb <dbdesc>
\end{lstlisting}
This will shutdown the database and call post\_dbstop stop.
\item Save dbsession before closing the dbsession. This option will automatically save the database session before releasing 
all the resources. To enable this, use the following option in addtion to launchdb command:
\begin{lstlisting}[style=mystyle]
--save_on_exit
\end{lstlisting}
\item To change number of hours the database session is active
  \begin{lstlisting}[style=mystyle]
--walltime <num_hours>
  \end{lstlisting}
  
\end{itemize}




All the rest of the commands have to executed from the compute node. For these login 
to the designated compute node using
\begin{lstlisting}[style=mystyle]
user@sfxlogin1: ssh <server_ip>
user@sfxlogin1: cd <your-work-directory>
user@sfxlogin1: . /home/pgxxc/public/dicex_pgsa/dicex_pgsa.sh
\end{lstlisting}

\paragraph{\question{How to stop the database instance?}}\hfill\\
\begin{lstlisting}[style=mystyle]
user@sfxlogin1: dicex_pgsa.sh --stopdb <session-identifier>
\end{lstlisting}
This will stop the database session.

\paragraph{\question{How to restart the database instance?}}\hfill\\
\begin{lstlisting}[style=mystyle]
user@sfxlogin1: dicex_pgsa.sh --restartdb <session-identifier>
\end{lstlisting}
This will restart the stopped the database session.

\paragraph{\question{How to save the database instance?}}\hfill\\
\begin{lstlisting}[style=mystyle]
user@sfxlogin1: dicex_pgsa.sh --savedb <session-identifier>
\end{lstlisting}
This will stop the database instance and save the image 

\paragraph{\question{How to  resume a saved  instance?}}\hfill\\
\begin{lstlisting}[style=mystyle]
user@sfxlogin1: dicex_pgsa.sh --resumedb <session-identifier>
\end{lstlisting}

\paragraph{\question{How to cleanup the database instance?}}\hfill\\
\begin{lstlisting}[style=mystyle]
user@sfxlogin1: dicex_pgsa.sh --cleandb <session-identifier>
\end{lstlisting}
This will stop the database and remove/delete the instance from the disk. 












\end{document}
